Child survival for mothers: mortality change and related measures

### 2020-04-07 draft.Rmd
Corrección párrafo
paper for ALAP Improving things

---
title: "Child survival for mothers: mortality change and related measures"
author: "Ivan Williams and Diego Alburez-Gutierrez"
date: "07 August 2019"
output: pdf_document
bibliography: bib.bibtex
---

@@

Where $H_{CS_a}$ can be interpreted as a temporary entropy constant until age $a-\alpha$. The age structure of the surviving daughters $C_{CS_a}(x)=\frac{m_{x}l_{a-x}}{CS_{a}}$ determines the contribution of each age to the disparity measure $H_{CS_a}=\int_\alpha^a{C_{CS_a}(x)H(x)}$ (@Aburto2019). The effect of a relative change $\delta$ on $C_{CS_a}$ will be stronger in cases where the mortality is more disperse at ages where fertility is high. Consider the two fertility schedules depicted in Figure \ref{fig:relative_change}. Against the backdrop of a mortality hump in early adulthood (dashed line), we anticipate a more pronounced change in $C_{CS_a}$ for the younger fertility schedule.

>>>>

---
title: 'Child survival for mothers: mortality change and related measures'
author: "Ivan Williams and Diego Alburez-Gutierrez"
date: "07 August 2019"
output:
  html_document:
    df_print: paged
bibliography: bib.bibtex
---

@@

Where $H_{CS_a}$ can be interpreted as a temporary entropy constant until age $a-\alpha$. The age structure of the surviving daughters $C_{CS_a}(x)=\frac{m_{x}l_{a-x}}{CS_{a}}$ determines the contribution of each age to the disparity measure $H_{CS_a}=\int_\alpha^a{C_{CS_a}(x)H(x)}$ (@Aburto2019). The effect of a relative change $\delta$ on $CS_{a}$ will be stronger in cases where the mortality is more disperse at ages where fertility is high. Consider the two fertility schedules depicted in Figure \ref{fig:relative_change}. Against the backdrop of a mortality hump in early adulthood (dashed line), we anticipate a more pronounced change in $C_{CS_a}$ for the younger fertility schedule.
